\documentclass[../CHEFCookingHelperForEveryonesFridge.tex]{subfiles}

\ifSubfilesClassLoaded{\raggedbottom}{}

\renewcommand{\thesubsection}{\arabic{subsection}.}

\begin{document}

\ifstrequal{\jobname}{TermsOfReference}{
    \newcommand{\ethicsSection}[1]{\subsection{#1}}
    \newcommand{\ethicsSectionStar}[1]{\subsection*{#1}}
}{
    \newcommand{\ethicsSection}[1]{\subsubsection{#1}}
    \newcommand{\ethicsSectionStar}[1]{\subsubsection*{#1}}
}
Student Project Ethics Approval Form
You should use this document if your project is not high-risk. Please complete this document and discuss your study
with your supervisor before you collect any data. \ul{\textit{Failure to complete this document and have all aspects signed
off and approved by your supervisor and 2nd marker results in a fail in your final module result and may risk a
case of Academic Misconduct.}}

Please ensure that your project meets the conditions of the existing module-level ethics application
(available on Blackboard). If it does not, then you will need to submit a full ethics application instead
via the main university ethics system.
\begin{table}[h!]
    \begin{tabulary}{\textwidth}{|l|L|}
        \hline
        Student Name: & Kieran Knowles \\\hline
        Student ID: & w20013000 \\\hline
        Programme Name: & BSc Computer Science \\\hline
        Project Title: & \chef{} - Cooking Helper for Everyone's Fridge \\\hline
        Supervisor Name: & Nick Dalton \\\hline
        Second Marker: & Marta Cecchinato \\\hline
        \makecell[l]{
            What type of study are you using \\
            (check all that apply):
        } &
            \checkbox{empty} Questionnaire or Survey \newline
            \checkbox{empty} User Studies \newline
            \checkbox{empty} Data Generated by Systems \newline
            \checkbox{checked} Secondary Data Analysis \newline
            \checkbox{empty} No data collected from humans \newline
        \\\hline
    \end{tabulary}
\end{table}


Please answer the following questions and complete all information in full:

\ethicsSection{Human Participants}
Does your study involve human participants \textbf{NO}


If \textbf{YES}, please answer the following questions and ensure that you include your participant
information sheet, participant consent sheet, and any participant recruitment materials/permission
letters for participants in Appendix B:

\begin{table}[H]
    \begin{tabulary}{\textwidth}{|L|L|}
        \hline
        1a) Who are your participants and what are the inclusion criteria you will be using? & Not Applicable \\\hline
        1b) How many participants will you recruit and from where? & Not Applicable \\\hline
        1c) Are there any exclusion criteria (reasons why people should not participate)? & Not Applicable \\\hline
    \end{tabulary}
\end{table}

\ethicsSection{Data Collection}
Will your study collect any primary data or use any secondary data not in the public domain? \textbf{NO}

Please complete the following questions, noting that somebody should be able to read this and replicate your approach:

\begin{table}[H]
    \begin{tabulary}{\textwidth}{|L|L|}
        \hline
        2a) What type of data are you going to use? (Identify main types of information/data)
            &
        A competitor analysis will be performed on existing applications and their user reviews will be consulted to determine requirements.
            \\\hline
        2b) What procedures will you use to collect data (include all equipment/methods you plan to use)
            &
        The publicly available applications of competitors will be analyzed to determine common features of the competitors that would be needed for \chef{}
        In addition, the user reviews of the competitors will be consulted to determine commonly requested features that could be added to \chef{}
            \\\hline
        2c) What methods will you use to analyze this data?
            &
        The features common to multiple competitors will be identified as part of the minimum viable product for \chef{}.
        Features requested by users will then be added to create the final product.
            \\\hline
    \end{tabulary}
\end{table}

\ethicsSection{}{Data Management}
Standard phrases have been added to the information sheet (available on Blackboard). In rare instances,
these may not be appropriate for your study. If not,
please describe any additional data management procedures below:

N/A - All data collected is publicly available.

\ethicsSection{}{Risk Assessment, Health and Safety}
All research activity carried out by Northumbria University is subject to risk assessment and health and safety
issues. Depending on the nature of your research work, you may need to use one of the risk assessments below
and/or complete a Project Risk Assessment in discussion with your supervisor. Once you have identified risks
and associated health and safety issues, you may need to consult relevant technical and other staff for further
advice and guidance. Further information including a blank risk assessment form for research can be found here:
\href{https://www.northumbria.ac.uk/about-us/health-safety-resources/risk-assessment/}{Risk Assessment (northumbria.ac.uk).}

Please check this box after you have read and understood ethics and health and safety information

\checkbox{checked}   I confirm I have read the University's health and safety policy and ethics policy.
I have read and understood the requirement for the mandatory completion of risk assessments and that my study
does not deviate from the module-level approval ethics information on Blackboard: Relevant risk assessments
are listed in the ethics application. If your project needs additional risk assessments, then you will need
to submit a new ethics application. Please identify the elements of the listed risk assessment that are relevant
to your study and the risk assessment(s) you are working with. Note that these are only relevant if you are
collecting data face-to-face.

Please check the relevant boxes:

\checkbox{checked}   No physical risks

\checkbox{empty}   HL\textunderscore RISK\textunderscore 173 Testing in an external environment

\checkbox{empty}   HL\textunderscore RISK\textunderscore 722 Face-to-face interview

\checkbox{empty}   HL\textunderscore RISK\textunderscore 727 Group interview

Supervisor (and/or Second Marker where appropriate) to assess using the following criteria:

\begin{table}[H]
    \begin{tabular}{|l|l|}
        \hline
        \multicolumn{2}{|l|}{Tutor sign off} \\\hline
        Ethics form complete & \checkbox{empty} \\\hline
        Ethical concerns acknowledged & \checkbox{empty} \\\hline
        Research tool(s) checked & \checkbox{empty} \\\hline
        All relevant forms included (consent etc.) & \checkbox{empty} \\\hline
        Is not high risk & \checkbox{empty} \\\hline
    \end{tabular}
\end{table}

\ethicsSectionStar{Appendix B: Participant Information \& Consent Form}
Note: this section MUST be completed if you are including human participants in your study

Please include here your participant information sheet, participant consent form plus any participant recruitment materials and permission letters.

N/A - No human participants are involved in this study.

\ethicsSectionStar{Appendix C: Risk Assessment Form}
If your project involves any health and safety risks, please also include a risk assessment form.

N/A - No human participants are involved in this study.

\end{document}
