\todoinline{
    Abstract
    The purpose of an abstract is to provide the reader with the essentials of your report in a very condensed form. (In a published paper, it would provide a basis for the
    reader to decide whether to read it or not). This means it should briefly summarise the nature of the project, its context, what work was carried out and what the major
    findings or conclusions were. Key technologies or approaches used will normally be mentioned. The marking schemes explain exactly what should be in your abstract. It must
    be no more than one side in length. It relates to completed work – it should not talk about what you are planning to do or the structure of the report. Write it last!
}

This project aimed to create a web application that allows users to find recipes based on the ingredients they have available
and to find similar recipes to those that were suggested. The application was built using a Node backend using Express and
a React frontend, both written in TypeScript. The backend uses a SQLite database to store all of its runtime data.

Requirements were gathered using a competitor analysis, a literature review, and use case analysis in the MoSCoW format before
being implemented. The backend was tested using Mocha and Supertest, with regression testing performed whenever an issue was
discovered. The frontend was tested manually to ensure that it met its requirements.

The final product was a prototype web application that met most of the core functional and non-functional requirements. The
application was designed to be extensible for future development, with the potential to be deployed publicly. However, certain
requirements were not implemented due to time constraints and would require further research before development. Overall, the
project has successfully satisfied its goals with the potential for future development.
