% Don't insert page breaks before these sections
{
\let\clearpage\relax

\section{The Final Product}

The project successfully created a prototype web application that allows users to search for recipes based on the ingredients they have available.
Most of the core functional and non-functional requirements discussed in Section~\ref{sec:requirements} were implemented, with the existing
framework being designed to be extensible for future development. The application is not deployed publicly, but can be run locally and would
be easy to deploy to the public.

\section{Deviations from the Original Plan}

Certain requirements were not implemented due to time constraints, shown in the requirements tables~\ref{tab:functional_requirements}
and~\ref{tab:non_functional_requirements} under the \enquote*{Implemented} column. While some of these would be easy to implement,
for example, the option to use imperial units, others would require significant research and refactoring, such as avoiding recipes too
similar to those recently made by the user.

Finally, the recipe search performance was not as fast as desired, with results taking multiple seconds to be returned, depending on the
server's performance. This was due to the query iterating over all recipes and evaluating similarity, taking $O(n)$ time, where $n$ is
the number of recipes in the database. A potential solution would have been to use a different database system optimized for such queries.

\section{Potential Future Work}

Future work would involve implementing the remaining requirements, and potentially migrating to a different database backend to improve
performance. Additionally, further competitor analysis could be performed to identify additional features to be implemented for a better
user experience.

} % <-- End of no-page-breaks section
